### 2016-06-22 stitched.tex
ENH:  Respnose to reviewers.

Random forests are conceptually straightforward\textsuperscript{17}.
They consist of ensembles of decision trees that are built from training
data. Once constructed, data to be classified is ``pushed'' through each
decision tree resulting in a single classification ``vote'' per tree.
These votes are then used for regression or classification of the data.
Although decision trees had been extensively studied, the success of
employing collections of such weak learners for boosting machine
learning performance (e.g., AdaBoost\textsuperscript{27,28}) influenced
the similarly sytled conglomeration of decision trees into ``forests''
with randomized node optimization\textsuperscript{29,30}. Finally,
Breiman\textsuperscript{17} improved accuracy by random sampling of
training data (i.e., ``bagging'') resulting in the current random forest
technique applied here.

@@

MR images utilized for this initial report were acquired from a single
scanner involved in the Chronic Effects of Neurotrauma Consortium's
(CENC) observational study (see Walker et al., this issue). Briefly,
participants were Operation Iraqi Freedom/Operation Enduring Freedom
(OIF/OEF) era Service Members and Veterans between the ages of 18-60
years with prior combat exposure and deployment(s). The feature images
consisted of 26 subjects aged 39.6 ± 8.1 years (range 28 -- 58 years).
Within this cohort, 24 (92\%) were considered positive for TBI based
upon the potential concussive events (PCE) interview process described
in detail in Walker et al., this issue). Each of the participants that
were selected from the larger cohort of participants in this study
demonstrated at least one white matter hyperintensity (but as many as
20) on FLAIR imaging.

Images were acquired on a Philips 3.0T Ingenia system with an 8-channel
SENSE head coil (Philips Medical Systems, Best, Netherlands). 3D FLAIR
sequences were acquired with a turbo spin echo inversion recovery
sequence with the following parameters: repetition time (TR) = 4800 ms,
echo time (TE) = 325 ms, inversion time (TI) = 1650 ms; 170 sagittal
slices with a 1.2 mm slice thickness, 256 x 256 acquisition matrix, and
256 x 256 mm FOV. 3D T1-weighted sequences were acquired with a fast
field echo (FFE) sequence with the following parameters: TR = 6.8 ms, TE
= 3.2 ms, echo train length (ETL) = 240; Flip angle = 9°, 170 sagittal
slices with a 1.2 mm slice thickness, 256x240 acquisition matrix, and
256 x 256 mm FOV. In addition, 3D T2-weighted images were acquired with
a turbo spin echo sequence with the following parameters: TR = 2500 ms,
TE = 245 ms, ET: = 133; 170 sagittal slices with a 1.2 mm slice
thickness, 256 x 256 acquisition matrix, and 256 x 256 mm FOV.

@@

@@

>>>>

Random forests are conceptually straightforward\textsuperscript{17}.
They consist of ensembles of decision trees that are built from training
data. Once \textcolor{blue}{the ensemble of decision trees is}
constructed, data to be classified is ``pushed'' through each decision
tree resulting in a single classification ``vote'' per tree. These votes
are then used for regression or classification of the data. Although
decision trees had been extensively studied, the success of employing
collections of such weak learners for boosting machine learning
performance (e.g., AdaBoost\textsuperscript{27,28}) influenced the
similarly sytled conglomeration of decision trees into ``forests'' with
randomized node optimization\textsuperscript{29,30}. Finally,
Breiman\textsuperscript{17} improved accuracy by random sampling of
training data (i.e., ``bagging'') resulting in the current random forest
technique applied here.

@@

MR images utilized for this initial report were acquired from a single
scanner involved in the Chronic Effects of Neurotrauma Consortium's
(CENC) observational study (see Walker et al., this issue). Briefly,
participants were Operation Iraqi Freedom/Operation Enduring Freedom
(OIF/OEF) era Service Members and Veterans between the ages of 18-60
years with prior combat exposure and deployment(s). The feature images
\textcolor{blue}{were derived from MR acquisitions of} 26 subjects aged
39.6 \(\pm\) 8.1 years (range 28--58 years). Within this cohort, 24
(92\%) were considered positive for TBI based upon the potential
concussive events (PCE) interview process described in detail in Walker
et al., this issue). Each of the participants that were selected from
the larger cohort of participants in this study demonstrated at least
one white matter hyperintensity (but as many as 20) on FLAIR imaging.

Images were acquired on a Philips 3.0T Ingenia system with an 8-channel
SENSE head coil (Philips Medical Systems, Best, Netherlands). 3D FLAIR
sequences were acquired with a turbo spin echo inversion recovery
sequence with the following parameters: repetition time (TR) = 4800 ms,
echo time (TE) = 325 ms, inversion time (TI) = 1650 ms; 170 sagittal
slices with a 1.2 mm slice thickness, 256 \(\times\) 256 acquisition
matrix, and 256 \(\times\) 256 mm FOV. 3D T1-weighted sequences were
acquired with a fast field echo (FFE) sequence with the following
parameters: TR = 6.8 ms, TE = 3.2 ms, echo train length (ETL) = 240;
Flip angle = 9\(^\circ\), 170 sagittal slices with a 1.2 mm slice
thickness, 256x240 acquisition matrix, and 256 \(\times\) 256 mm FOV. In
addition, 3D T2-weighted images were acquired with a turbo spin echo
sequence with the following parameters: TR = 2500 ms, TE = 245 ms, ET: =
133; 170 sagittal slices with a 1.2 mm slice thickness, 256 \(\times\)
256 acquisition matrix, and 256 x 256 mm FOV.

@@

\textcolor{blue}{Figure X provides a graphical overview of the proposed workflow.  The major components
include offline generation of symmetric multimodal templates, the creation of
feature images from the training data which are then used to model the statistical
prediction using a concatenated random forest framework.  Once these offline steps
are performed, a new, unsegmented subject can then be processed using the proposed pipeline.}

@@

\textbf{Figure X:}
\textcolor{blue}{Workflow illustration for the proposed pipeline.  Processing of the multi-modal
input MRI for a single subject, using the multi-modal symmetric template, results in
the generation of the feature images.  These feature images are used as input to the
Stage 1 RF model producing the initial RF probability map estimates.  The Stage 1
voting maps, the original feature images, and the Stage 2 RF model result in the
final voting maps which includes the WMH probability estimate.  Note that the RF models
are constructed once from a set of training data which are processed using the
same feature-construction pipeline as the single-subject input MRI.}
